data import

### 2022-11-14 r-imports/data.Rmd
backlog

download.file("https://zenodo.org/record/6483002/files/essd_ghg_data_gwp100.xlsx?download=1","data-raw/gwp100.xlsx")
download.file("https://zenodo.org/record/7190601/files/LULUCF%20NGHGI%20database%20August%202022.xlsx?download=1","data-raw/lulucf.xlsx")

>>>>

download.file("https://zenodo.org/record/6483002/files/essd_ghg_data_gwp100.xlsx?download=1","data-raw/gwp100.xlsx")
#download.file("https://zenodo.org/record/7190601/files/LULUCF%20NGHGI%20database%20August%202022.xlsx?download=1","data-raw/lulucf.xlsx")
